---
title: "My Fancy Presentation"
author: "Marcela Castro León"
date: "April 12, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## My new slide
some content

*** 
a slide without title

## My title

### a top level subheading

#### a new sublevel heading

## bullets and items

- bullet one
- bullet two

1. Item a
2. Item b

## using bold and italics

Plain text
*italics*
**bold text**

`for(i %in% 1:10)`

## using r

```{r,comment= "", echo = FALSE}
head(mtcars)
```

## using plot

```{r,  echo = FALSE, fig.align='center', fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

